Object naming is context dependent - A case study on testing linguistic hypotheses on real-world image corpora

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex
Adds practical requirements for datasets

\begin{itemize}
        \item[(1)] \textbf{Lexical choice}: \\
        Which name did the speaker use to refer to the target object?
		\item[(2)] \textbf{Lexical candidates}: \cs{"candidate" does not exclude the chosen name in contrast to "alternative"}\\
		%Which names are available for the target objects?  
		Which names are available for the target objects? 
		And how are they taxonomically related? 
		For instance, if we want to check whether a convertible is more often referred to with a basic-level category (e.g.,~\refexp{car}) or a more specific one (e.g.,~\refexp{convertible}) we need to know that a given object is a \cat{convertible}, and that \cat{convertible} is a sub-level concept of \cat{car} (and \cat{vehicle}, etc.). 
		%Additionally, in
		In \cite{graf2016animal}, the authors manually group object names used by speakers in terms of three levels (sub-level, basic-level, super-level). 
		Thus, ideally, %names 
		lexical candidates 
		would be grouped according to their taxonomic relations. 
		\item[(3)] \textbf{Contextual informativeness}: \\
		Which names are available for the other objects in the scene (i.e. distractors)?
		For instance, when the target is a \cat{convertible}, we need to know that there are multiple \cat{convertibles}, \cat{cars}, etc. to judge whether these concepts are ambiguous.
\end{itemize}

\cs{Should the following be here or at the beginning of Sect. 4?}
\cs{We could also call below requirements "Desiderata"}
In practical terms, the prerequisite for Requirements~(2) and~(3) is, given an image, the information on \textbf{R1: the most specific category} of \textbf{each object} which is depicted in the image. 
A taxonomy, such as WordNet \cite{fellbaum1998wordnet}, could then be queried with these categories to retrieve their individual lexical candidates arranged by their taxonomic relations. \\
Furthermore, the information on the \textbf{R2: entry-level category} of an object could be used as a pivot to taxonomically group its lexical candidates.

>>>>

\begin{itemize}
        \item[(1)] \textbf{Lexical choice}: \\
        Which name did the speaker use to refer to the target object?
		\item[(2)] \textbf{Lexical candidates}: \\
		%Which names are available for the target objects?  
		Which names are applicable to the target objects? 
		And how are they taxonomically related? 
		For instance, if we want to check whether a convertible is more often referred to with a basic-level category (e.g.,~\refexp{car}) or a more specific one (e.g.,~\refexp{convertible}) we need to know that a given object is a \cat{convertible}, and that \cat{convertible} is a sub-level concept of \cat{car} (and \cat{vehicle}, etc.). 
		%Additionally, in
		In \cite{graf2016animal}, the authors manually group object names used by speakers in terms of three levels (sub-level, basic-level, super-level). 
		Thus, ideally, %names 
		lexical candidates 
		would be grouped according to their taxonomic relations. 
		\item[(3)] \textbf{Contextual informativeness}: \\
		Which names are applicable for the other objects in the scene (i.e. distractors)?
		For instance, when the target is a \cat{convertible}, we need to know if there are multiple \cat{convertibles}, \cat{cars}, etc. to judge whether these concepts are ambiguous.
		%We are required to have this information in order to judge whether a certain name would be informative in a certain context, i.e., whether it would apply uniquely to the target object.
\end{itemize}

\cs{Should the following be here or at the beginning of Sect. 4?}
\cs{We could also call below requirements "Desiderata"}
In practical terms, the prerequisite for Requirements~(2) and~(3) is, given an image, the information on \textbf{R1: the most specific category} of \textbf{each object} which is depicted in the image. 
A taxonomy, such as WordNet \cite{fellbaum1998wordnet}, could then be queried with these categories to retrieve their individual lexical candidates arranged by their taxonomic relations. \\
Furthermore, the information on the \textbf{R2: entry-level category} of an object could be used as a pivot to taxonomically group its lexical candidates.  
Under the assumption that the entry-level, as the preferred level of specificity, is produced most often for an individual concept, may be inferrable from the data itself through maximum likelihood estimation. 
For example, based on frequency estimates, the entry-level for the object on the left is \refexp{dalmatian} (Figure~\ref{fig:ex_visualgenome}), whereas the object on the right is referred to by \refexp{heeler} once, and mostly by \refexp{dog} and its appearance or location.
